---
pagetitle: "Population Genomics In Practice H25"
toc: false
date: last-modified
sidebar: false
format:
  nbis-course-html:
    number-sections: false
    template-partials:
      - assets/www/title-block.html
execute:
  freeze: false
  cache: false
---



```{r }
#| label: load-course-date-info
#| echo: false
#| eval: true
library(lubridate)
library(dplyr)
library(kableExtra)
library(formattable)
library(yaml)

current <- yaml::read_yaml("_course_info.yml")$current
session <- yaml::read_yaml("_course_info.yml")[[as.character(current)]]
if (grepl("TBA$", current)) {
  current <- "(To be announced)"
}
```

### NBIS • Workshop

### DDLS Population genomics in practice

Welcome to the DDLS Population Genomics in Practice homepage!

#### Important dates and information

See the canvas home page for the current course
[`r current`](`r session$canvas_home_page`) for more
information on how to apply.

```{r }
#| label: print-course-dates
#| echo: false
#| eval: true
#| results: asis
df <- data.frame(
  title = c("Next round", "Application opens", "Application deadline"),
  data = c(
    paste0(
        format(as_datetime(session$start_time), "%d-%b-%Y"),
        " - ",
        format(as_datetime(session$end_time), "%d-%b-%Y")
    ),
    format(as_datetime(session$application_opens), "%d-%b-%Y"),
    format(as_datetime(session$application_closes), "%d-%b-%Y")
  )
)
cat(
  print(kable(df,
    format = "pipe", escape = FALSE,
    row.names = FALSE, col.names = NULL,
    align = c("l", "c")
  )),
  "\n\n: {.hover .condensed .responsive}\n\n"
)
```

#### Brief contents

:::: {.columns}

::: {.column width="50%"}

This workshop includes the following moments:

- Variant calling and filtering
- Describing and summarising variation data
- Population structure
- Demographic analysis
- Selection scans
- Coalescent simulation

See [syllabus](syllabus.qmd) for a more complete description of course
contents and [info](info.qmd) for practical information on venue and
hotels.

:::

::: {.column width="50%"}

![](img/ooa-demesdraw-fig-1.svg){height="600px"}

:::

::::

#### Course archive

- [DDLS Population Genomics In Practice 2023](https://nbisweden.github.io/workshop-pgip/)

<br>

![](assets/logos/nbis-scilifelab.svg){height="1.2em"}

<br>

---

::: {.landing-update}

::: {.smallest}

Last updated on {{< fa calendar-alt >}} {{< meta date >}}

:::

:::
