---
pagetitle: "Population Genomics In Practice H25"
toc: false
date: last-modified
sidebar: false
format:
  nbis-course-html:
    number-sections: false
    template-partials:
      - assets/www/title-block.html
execute:
  freeze: false
  cache: false
include-in-header:
  - text: |
      <style>.logo { padding: 3em 0 .3em 0; }</style>
---

# NBIS • Workshop

```{r }
#| label: load-course-date-info
#| echo: false
#| eval: true
library(lubridate)
library(dplyr)
library(kableExtra)
library(formattable)
library(yaml)

current <- yaml::read_yaml("_course_info.yml")$current
session <- yaml::read_yaml("_course_info.yml")[[as.character(current)]]
if (grepl("TBA$", current)) {
  current <- "(To be announced)"
}
```

## Population genomics in practice

Welcome to the Population Genomics in Practice homepage!

This site contains general information about the course. For current
course round material, navigate to
<https://nbisweden.github.io/workshop-pgip-H25>.

### Important dates and information

See the canvas home page for the current course
[`r current`](`r session$canvas_home_page`) for more
information on how to apply.

```{r }
#| label: print-course-dates
#| echo: false
#| eval: true
#| results: asis
df <- data.frame(
  title = c("Next round", "Application opens", "Application deadline"),
  data = c(
    paste0(
        format(as_datetime(session$start_time), "%d-%b-%Y"),
        " - ",
        format(as_datetime(session$end_time), "%d-%b-%Y")
    ),
    format(as_datetime(session$application_opens), "%d-%b-%Y"),
    format(as_datetime(session$application_closes), "%d-%b-%Y")
  )
)
cat(
  print(kable(df,
    format = "pipe", escape = FALSE,
    row.names = FALSE, col.names = NULL,
    align = c("l", "c")
  )),
  "\n\n: {.hover .condensed .responsive}\n\n"
)
```

### Brief contents

:::: {.columns}

::: {.column width="50%"}

This workshop includes the following moments:

- Variant calling and filtering
- Describing and summarising variation data
- Population structure
- Demographic analysis
- Selection scans
- Coalescent simulation

See [syllabus](syllabus.qmd) for a more complete description of course
contents and [info](info.qmd) for practical information on venue and
hotels.

:::

::: {.column width="50%"}

![Demesdraw image of out of Africa
model.](img/ooa-demesdraw-fig-1.svg){height="600px"}\

:::

::::

### Course material

::: {.callout-important icon=false .large}

A link to course material will be added soon.

:::

### Course archive

- [DDLS Population Genomics In Practice 2023](https://nbisweden.github.io/workshop-pgip-H23/)

:::{.logo}

![NBIS scilifelab combined logo.](assets/logos/nbis-scilifelab.svg){height="1.2em"}\

:::

---

::: {.landing-update}

::: {.smallest}

Last updated on {{< fa calendar-alt >}} {{< meta date >}}

:::

:::
